Analysis

### 2017-03-25 Analysis.Rmd
Correct errors in Analysis.Rmd

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# Diagnostic line plots for treatements
ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# joint distibution of error
rdf <- data.frame(LShB_lmm_2015$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1)
```

@@

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# Diagnostic line plots for treatments
ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# joint distibution of error
rdf <- data.frame(TShB_lmm_2015$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1)
```

@@

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# Diagnostic line plots for treatments
ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# joint distibution of error
rdf <- data.frame(TShB_lmm_2015$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1)

@@

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# Diagnostic line plots for treatments
ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .)

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte()

# joint distibution of error
rdf <- data.frame(TShB_lmm_2015$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1)
```

>>>>

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2015 Leaf Sheath Blight Replicates")

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2015 Replicate Posteriors for Leaf Sheath Blight")

# Diagnostic line plots for treatments
ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2015 Leaf Sheath Blight Treatments")

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2015 Treatment Posteriors for Leaf Sheath Blight")

# joint distibution of error
rdf <- data.frame(LShB_lmm_2015$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("2015 Leaf Blight Error") +
  theme_tufte()
```

@@

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2015 Tiller Sheath Blight Replicates")

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2015 Replicate Posteriors for Tiller Sheath Blight")

# Diagnostic line plots for treatments
ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2015 Tiller Sheath Blight Treatments")

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2015 Treatment Posteriors for Tiller Sheath Blight")

# joint distibution of error
rdf <- data.frame(TShB_lmm_2015$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("2015 Tiller Blight Error") +
  theme_tufte()
```

@@

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2016 Leaf Sheath Blight Replicates")

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2016 Replicate Posteriors for Leaf Sheath Blight")

# Diagnostic line plots for treatments
ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2016 Leaf Sheath Blight Treatments")

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2016 Treatment Posteriors for Leaf Sheath Blight")

# joint distibution of error
rdf <- data.frame(LShB_lmm_2016$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("2016 Leaf Blight Error") +
  theme_tufte()

@@

# Diagnostic line plots for replicate
ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2016 Tiller Sheath Blight Replicates")

# Posterior distributions for replicate
ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2016 Replicate Posteriors for Tiller Sheath Blight")

# Diagnostic line plots for treatments
ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
  geom_line() +
  theme_tufte() +
  xlab("Iteration Number") +
  ylab(NULL) +
  facet_grid(variable ~ .) +
  ggtitle("Diagnostic Plots for 2016 Tiller Sheath Blight Treatments")

# Posterior distributions for treatment
ggplot(trts, aes(x = value, color = variable)) + 
  geom_density() +
  theme_tufte() +
  ggtitle("2016 Treatement Posteriors")

# joint distibution of error
rdf <- data.frame(TShB_lmm_2016$VCV)
ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
  geom_density2d() + 
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("2016 Tiller Sheath Blight Error") +
  theme_tufte()
```
